Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2023-07-03 src/docs_paper/appendix.Rmd
Add time taken to draft #55

```{r}
ks_summary <- readRDS("depends/ks_summary.rds")

ks_summary %>%
  filter(Type == "Latent field") %>%
  group_by(Parameter) %>%
  summarise(
    `D(TMB)` = round(mean(`KS(TMB, tmbstan)`), 3),
    `D(PCA-AGHQ)` = round(mean(`KS(aghq, tmbstan)`), 3)
  ) %>%
  gt::gt(rowname_col = "Parameter") %>%
  gt::summary_rows(
   columns = everything(),
   fns = list(Average = ~ mean(.x)),
   formatter = gt::fmt_number,
   decimals = 3
  )
```

>>>>

```{r}
ks_summary <- readRDS("depends/ks-summary.rds")

ks_summary %>%
  ungroup() %>%
  filter(type == "Latent field") %>%
  select(-type) %>%
  gt::gt(rowname_col = "Parameter") %>%
  gt::summary_rows(
   columns = everything(),
   fns = list(Average = ~ mean(.x)),
   formatter = gt::fmt_number,
   decimals = 3
  )
```

### 2023-07-03 src/docs_paper/paper.Rmd
Add time taken to draft #55

@@

1. TMB,
2. PCA-AGHQ, via extension of the `aghq` package [@stringer2021implementing],
3. NUTS: the Hamiltonian Monte Carlo (HMC) algorithm No-U-Turn Sampling (NUTS) using Stan [@carpenter2017stan] via the `tmbstan` package [@monnahan2018no].

>>>>

```{r}
time_taken <- read_csv("depends/time-taken.csv")
```

@@

1. TMB (`r signif(time_taken$TMB, 2)` seconds)
2. PCA-AGHQ (`r signif(time_taken$aghq, 2)` hours), implemented via extension of the `aghq` package [@stringer2021implementing],
3. NUTS (`r signif(time_taken$tmbstan, 2)` days), the Hamiltonian Monte Carlo (HMC) algorithm No-U-Turn Sampling (NUTS) using Stan [@carpenter2017stan] implemented via the `tmbstan` package [@monnahan2018no].
